%______________________________________________________________________________________________________________________
% @brief LaTeX2e Resume for Rui Jiang
\documentclass[margin,line]{resume}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Huge{Rui Jiang}}
\begin{resume}
%__________________________________________________________________________________________________________________
% Contact Information
\section{\mystyle Contact\\Information}
E-mail: rui.gary.jiang@gmail.com\hfill Github Profile: github.com/ja67

%__________________________________________________________________________________________________________________
% Education
\section{\mystyle Education}%\mysidestyle
\begin{list2}
\item M.S. in Computer Science, University of California, Los Angeles\hfill \textsl{Sep.2012 - Apr.2014}
\item  Overall GPA: 3.675/4 \hfill
\item B.S. in Automation, Shanghai Jiao Tong University GPA:85.17/100\hfill \textsl{Sep.2008 - Jun.2012}
\end{list2}
%__________________________________________________________________________________________________________________
% Research Interests
\section{\mystyle Professional Skills}
\begin{list2}
\item Programming Language: Python(Flask), SQL, HTML, CSS, JavaScript(AngularJS), Bash, C\#, C++
\item Database: MySQL, PostgreSQL, Redis, AWS Redshift and DynamoDB, Microsoft SQL Server
\item Development Operation Tools: Amazon Web Service, Docker, Fabric
\end{list2}
%__________________________________________________________________________________________________________________
%Research&Professional Experience
\section{\mystyle Work Experience}
\textbf{Software Engineer in OpenMail LLC}\hfill
\textsl{Feb.2015 - }
\begin{list2}
\item Full stack web application development, including backend development of server side RESTful-API using Python and Flask web framework and frontend development under framework(AngularJS)
\item Software architecting and development of one of the core backend projects managing external resources using asynchronous API and task queue
\item Write unit test and integrate QA test for backend(Pytest) and frontend(Karma and Jasmine framework and protractor) functions
\item Manage the codebase of the project using version control Git to ensure the quality and orderliness of the code
\item Development operation and system maintenance based on AWS cloud service. Deployment of server using Docker
\item Gather feedback from users and give suggestions about feasibility of product design to improve user experience
\item Setting up alerts and logs to monitor server status. Handle pages and fix any emergency issues once every two month
\end{list2}
\textbf{Software Engineer in Laserfiche}\hfill
\textsl{May.2014 - Feb.2015}
\begin{list2}
\item Implemented a collaberative real-time editor based on Etherpad
written in Node.js and also build some plugins for improvement.
\item Created an HTML5 E-Document viewer web app that supports PDF and other
Microsoft Office document formats with sufficient functions using C\# as
backend. It is embedded in Laserfiche Answers site and product.
\item Created a .NET tool library that packets documents and generate a brochure
from them. This is integrated in Laserfiche document management system.
\end{list2}
%__________________________________________________________________________________________________________________

\section{\mystyle Research Experience}
\textbf{Pattern Recognition and Computer Vision}\\
\textit{3D Simultaneous Mapping and Model Reconstruction Graduate Project in UCLA}
\begin{list2}
\item PI: Prof Songchun Zhu
\item Developed a real-time program generating 3D indoor model based on RGB and
depth frames collected by Kinect for object recognition.
\end{list2}
\textit{IBM Waston "The Great Mind Challenge" Machine
Learning Championship}
\begin{list2}
\item PI: Prof Songchun Zhu
\item Wrote programs aiming to get answer of 'Jeopathy' automatically. Built the essential part of the
solution, a two-level classier using decision trees and Logic Regression.Team ranked 1st.
\end{list2}

%______________________________________________________________________________________________________________________
% Publications
\section{\mystyle Publications}
\begin{list2}
\item Rui Jiang and Bing Han, Soft Landing Process Control of Chang’E 3 Lunar Probe and Software Simulation, Accpeted by Journal of Microcomputer Applications
\end{list2}
%__________________________________________________________________________________________________________________
% Honors and Awards
\section{\mystyle Honors\&\\Awards}
\begin{list2}
\item Academic Excellence Scholarship (Third-Class) of SJTU \hfill {2008 - 2009}
\end{list2}
\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF

